%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Professional CV
% LaTeX Template
% Version 2.0 (8/5/13)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rishi Shah 
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Ramesh S} % Your name
\address{Mgr nager,2 main road,thiruporur.Chennai.603110} % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
\address{(+91)9150388374 \\ rameshseerangan70@gmail.com} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf Hindustan institute of technology and science, Chennai} \hfill {\em August 2022 - May 2024} 
\\ Master's of Computer Applications.\hfill { Overall CGPA: 8.9 }

{\bf Hindustan institute of technology and science, Chennai} \hfill {\em July 2019 - June 2022} 
\\ Bachelor of Computer application, Civil.\hfill { Overall CGPA: 7.52 }
%Minor in Linguistics \smallskip \\
%Member of Eta Kappa Nu \\
%Member of Upsilon Pi Epsilon \\


\end{rSection}

\begin{rSection}{Carrier Objective}
 To work for an organization which provides me the opportunity to improve my skills and knowledge to grow along with the organization objective.
\end{rSection}
%--------------------------------------------------------------------------------
%    Projects And Seminars
%-----------------------------------------------------------------------------------------------
\begin{rSection}{Projects}
{\bf Smart hotel analysed based on tokenization
and lemmatization a recommendation system:}
\\The project gathers extensive data from various hotels, enriched by user input for personalized recommendations. It integrates user preferences to match travelers' lodging needs, addressing the challenge of selecting the ideal hotel for specific trip dates. Emphasizing data preparation, the project uses the NLTK package in Python for advanced text data handling. A key deliverable is a user interface showing a curated list of the top five hotels that best meet user needs. \\
\\{\bf Classification Of Melanoma Skin
Cancer Using -CNN}\\
Skin cancer is one of the deadliest illnesses globally. Early diagnosis of skin lesions can significantly improve treatment outcomes. However, the scarcity and imbalance of skin illness photos used for training make automated skin cancer classification challenging. Recent studies have utilized deep learning-based techniques to address these issues effectively. This study focuses on skin cancer classification using CNN learning models, achieving an accuracy of 82 Percentage.\\

\end{rSection}
%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Technical Strengths}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Programming Languages  \ & Python, Html, CSS, Sql,javascript, Tailwind CSS \\
Frameworks  \ & Django. \\
Development  \ & Full Stack Development, Website Development, UI Design. \\
Software \& Tools & MS-Office, VS-Code, Jupyter Notebook. \\
Soft Skills  \ &Problem Solving, Time Management, Analytical Skills.
\\
Data Analysis \ & Data Collection, Data Pre-processing.Data cleaning. \\

\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{INTERNSHIP}

\begin{rSubsection}{Tech-no-Hacks}{August 2023}{Python}{}
\item Developed a basic calculator application in Python,
Created an ATM simulator program to handle banking transactions,
Implemented a temperature conversion tool between Celsius and Fahrenheit.
\end{rSubsection}

\end{rSection}


%	EXAMPLE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{CERTIFICATIONS} 
\item Python programming at Htop Solution - July 2022
\item MERN Full Stack development at Guvi - Pursuing 
\end{rSection}

\end{document}
